---
title: "Aides Drug"
author: "MarenaO"
date: "Spring 2022 Semester"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
triUmp <-read.csv(file="triUmpsal.csv",header=TRUE)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative aides drug (triUmpsal) is under test in clinical trials. Consider only the females, does this drug seem effective?  Hint - use dplyr to obtain that subpopulation with the filter command.

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

```{r}
females<- filter(triUmp, gender == "F")
```


# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~infected + treatment,data=females)
barchartGC(~infected + treatment,data=females, type="percent")

```

According to the graphical data, the drug does not seem to be working for the females.The bar for the drug was higher than the bar for the placebo, meaning it was not as effective at preventing aids.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
table1 <- xtabs(~infected + treatment, data=females)
rowPerc(table1)
colPerc(table1)
```

The numerical data confirms that for the females, taking the drug is not helping with aids. The numerical data shows that around 59% of the females got aids that tpook the drug, and around 41% of the females who took the placebo got aids. Essentially, the drug does not seem to be working for the females, but it is making them get aids rather than helping to prevent aids.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

The Fisher's Exact Test tells us the odds of getting aids if you take the drug. The test shows that the odds of a female getting aids is 1.5 to 1. The odds should not be greater, they should be less, therefore, this test confirms that the drug is not working for the females. 

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
